Journey: A Study of Scalabilty of Memory Management in Linux (TODO: should we get a new title?)

### 2017-04-28 paper.tex
make changes to mmap latency conclusion

TODO?

>>>>

The kernel latency of m-mapping a memory region is lowest when the new memory is allocated
next to an already allocated region. This latency is the worst in the frag microbenchmark i.e., when an already mapped region
is to be expanded. We suspect a lot of real world applications to show the fragmented 
behavior since it is common for applications to exapnd their existing data structures. 
This finding highlights
the imporance of optimistically leaving empty spaces around the allocated regions to 
speed up memory expension. This practice would particularly be useful for performance crucial applications
running atop compute infrastructures where memory is not a scarce resource but kernel is.
